Exploring probability distributions for bivariate temporal granularities

### 2019-12-16 main.Rmd
minor corrections

- Data: <$C_1$, $C_2$, $v$>
- Aesthetic mapping: $C_1$ mapped to $x$ position and $v$ to $y$ position
- Statistical transformation: Any descriptive or smoothing statistics that summarizes distribution of $v(s)$
- Geometric objects: Any geometry displaying distribution, for example, boxplot, letter value, violin, ridge or highest density region plots
- Facet:  $C_2$

@@

<!-- Hence, the ingredients for the plots are subsets of numbers (or categorical measurements), and the choice of faceting or axis alignment for the subset strata. The basic plot choice is display of density. Different plots might be appropriate depending on which features of the density we are interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization. While we accomplish that, we need to bear in mind that any customized species of visualization might be constructed by varying the set of mappings between data properties and visual attributes such as position, shape and color. We are trying to address problems where even with good aesthetic qualities and good data, the graph might be confusing or misleading because of how people process the information. -->

@@

When we consider the layers of grammars considered for our data structure <$A_i$, $B_j$, $v(s)$> $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$, mapping $A_i$ mapped to $x$ position and $B_j$ to facets
suggests that levels of $C_1$, that is $A_i$'s which are placed in close proximity are to be compared against each other and each level of $B_j$ represent a group. When $A_i$ mapped to facets and $B_j$ is mapped to $x$ axis, distributions are compared across levels of $B_j$ and levels if $A_i$ start acting as a group. However, the variables used in the layers are the same, the difference in mapping emphasizes different behavior of the variables.

>>>>

- Data: <$C_1$, $C_2$, $v$>
- Aesthetic mapping: $C_1$ mapped to $x$ position and $v$ to $y$ position
- Statistical transformation: Any descriptive or smoothing statistics that summarizes distribution of $v$
- Geometric objects: Any geometry displaying distribution, for example, boxplot, letter value, violin, ridge or highest density region plots
- Facet:  $C_2$

@@

<!-- Hence, the ingredients for the plots are subsets of numbers (or categorical measurements), and the choice of faceting or axis alignment for the subset strata. The basic plot choice is display of density. Different plots might be appropriate depending on which features of the density we arae interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization. While we accomplish that, we need to bear in mind that any customized species of visualization might be constructed by varying the set of mappings between data properties and visual attributes such as position, shape and color. We are trying to address problems where even with good aesthetic qualities and good data, the graph might be confusing or misleading because of how people process the information. -->

@@

When we consider data sets of the form <$C_1$, $C_2$, $v$> with $C_1$ mapped to $x$ position and $C_2$ to facets
$A_i$'s are placed in close proximity and each $B_j$ represent a group/facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, in this case $A_i$'s are compared against each other within each group. When $C_2$ is mapped to facets and $C_1$ is mapped to $x$ axis, comparisons would ideally happen across all $B_j$ within each $A_i$. Although the variables used in the layers are the same, the difference in mapping leads to emphasis of different behavior of the variables.
